Laplacian envelope

### 2021-10-11 Notes/laplace.tex
simpler heuristic envelope

We can maximise this \wrt \(\varepsilon\).
We define
%
\begin{equation*}
\begin{aligned}
  \Delta m &= (m-1), &
  \mu &= \frac{m}{\Delta m}, \\
  \Delta f_m(\beta) &= S((m-1)\beta), &
  f_m(\beta) &= \frac{S(m\beta)}{\Delta f_m(\beta)}, \\
  \Delta g_m(\beta) &= \Delta f_m(\beta) + 1 , &
  g_m(\beta) &= \frac{S(m\beta) + 1}{\Delta g_m(\beta)}, \\
\end{aligned}
  \; \implies \quad
  \hat{A}(s) = \frac{\Delta f_m (1 - \varepsilon) (f_m - \varepsilon)}
                    {s \Delta m \Delta g_m (\mu - \varepsilon) (g_m - \varepsilon)}.
\end{equation*}
%
The maximum is at
%
\begin{equation}\label{eq:stickyopt}
\begin{aligned}
  % \brk{(1 + f_m -  g_m - \mu)\varepsilon - f_m + \mu g_m}^2 
  %   = (\mu - 1) (g_m - 1) (f_m - \mu) (f_m - g_m) , \\
  \varepsilon &= \frac{f_m - \mu g_m 
        \pm \sqrt{(\mu - 1) (g_m - 1) (f_m - \mu) (f_m - g_m)}}
      {1 + f_m -  g_m - \mu} \\
  \implies \qquad
  \hat{A}(s) &= \frac{\Delta f_m}{s \Delta m \Delta g_m}
      \brk{\frac{\sqrt{(f_m - \mu)(f_m - g_m)} 
                  + \sqrt{(\mu - 1)(g_m - 1)}}
                {\sqrt{(f_m - g_m)(g_m - 1)} 
                  + \sqrt{(f_m - \mu)(\mu - 1)}}}^2.
\end{aligned}
\end{equation}
%
The result is plotted in \cref{fig:sticky}.

@@

We will phrase it in terms of \(\snrb(\tau)\), reintroducing \(r\):
%
\begin{equation}\label{eq:envunits}
  \snrb(\tau) = \frac{ \sqrt{N} \hat{A}\prn{\frac{1}{r\tau}} }{ r\tau },
  \qquad
  \beta(\tau) = \sinh\inv \!\!\sqrt{1/2r\tau}.
\end{equation}
%
Then, combining \cref{eq:binaryenv,eq:unienv,eq:stickylaplace}, using the notation \( \Delta_{\varepsilon}[T(M)] = T(M) - \varepsilon T(M-2) \) for any function \(T(M)\), we find
%
\begin{equation}\label{eq:henv}
  \snrb(\tau) = \left\{
\begin{aligned}
  & \frac{\sqrt{N}}{1+r\tau}, &
  & r\tau \leq \tfrac{1}{2\sinh^2\frac{y_*}{2}} , \\
  & \sqrt{N}\prn{ \frac{ 4\sinh^2 \frac{y_*}{2} }{ y_* \cosh y_* } } \beta(\tau), &
  \tfrac{1}{2\sinh^2 \frac{y_*}{2}} \leq & r\tau \leq \tfrac{1}{2\sinh^2 \frac{y_*}{M}} , \\
  & \max_{\varepsilon \in [0,1]} \brc{
      \frac{2\sqrt{N}(1-\varepsilon) \Delta_{\varepsilon}\brk{S\prn{\tfrac{M\beta}{2}}}}
      {\Delta_{\varepsilon}\brk{M} \Delta_{\varepsilon}\brk{S\prn{\tfrac{M\beta}{2}} + 1} } 
      }, &
  \tfrac{1}{2\sinh^2 \frac{y_*}{M}} \leq & r\tau ,
\end{aligned}
\right.
\end{equation}
%
where \(\beta(\tau)\) and \(S(\beta)\) are given by the second formula of \cref{eq:detagensol}.

For \(M \gg 1\), and \(r\tau\) much greater than the lower bound of each region, we can approximate the envelope as
%
\begin{equation}\label{eq:henvapprox}
  \snrb(\tau) \approx \left\{
\begin{aligned}
  & \frac{\sqrt{N}}{1+r\tau}, &
  & r\tau \leq 0.73 , \\
  & \frac{ 0.54\sqrt{N}}{ \sqrt{r\tau} } , &
  0.73 \leq & r\tau \leq 0.22 M^2 , \\
  & \frac{ \sqrt{N} (M-1) }{ r\tau }, &\quad
  0.22 M^2 \leq &r\tau .
\end{aligned}
\right.
\end{equation}
%
This is plotted in \cref{fig:heuristicenv}.
It should be compared to \cref{eq:env,eq:envDB}.
\Cref{eq:henvapprox} has a similar form as \cref{eq:envDB}.
The left edge of the middle section is at later times in the theoretical version if \(\gamma \gtrsim \frac{1}{2} \csch^2 \frac{y_\ast}{2} \approx 0.73 \).
The right edge of the middle section is at later times in the theoretical version if \(\gamma \lesssim 2 y_\ast^2 \approx 4.53 \).
The middle section has greater \(\snrb\) in the theoretical version if \(\gamma \gtrsim \frac{8\sinh^2y_\ast}{\cosh^4y_\ast} \approx 1.18 \).

>>>>

We can maximise this \wrt \(\varepsilon\).
% We define
% %
% \begin{equation*}
% \begin{aligned}
%   \Delta m &= (m-1), &
%   \mu &= \frac{m}{\Delta m}, \\
%   \Delta f_m(\beta) &= S((m-1)\beta), &
%   f_m(\beta) &= \frac{S(m\beta)}{\Delta f_m(\beta)}, \\
%   \Delta g_m(\beta) &= \Delta f_m(\beta) + 1 , &
%   g_m(\beta) &= \frac{S(m\beta) + 1}{\Delta g_m(\beta)}, \\
% \end{aligned}
%   \; \implies \quad
%   \hat{A}(s) = \frac{\Delta f_m (1 - \varepsilon) (f_m - \varepsilon)}
%                     {s \Delta m \Delta g_m (\mu - \varepsilon) (g_m - \varepsilon)}.
% \end{equation*}
%
The maximum is at
%
\begin{equation}\label{eq:stickyopt}
\begin{aligned}
  % \brk{(1 + f_m -  g_m - \mu)\varepsilon - f_m + \mu g_m}^2 
  %   = (\mu - 1) (g_m - 1) (f_m - \mu) (f_m - g_m) , \\
  \varepsilon 
    % &= \frac{f_m - \mu g_m 
    %     - \sqrt{(\mu - 1) (g_m - 1) (f_m - \mu) (f_m - g_m)}}
    %   {1 + f_m -  g_m - \mu} \\
    &= \frac{D - S(m\beta)}{D - S((m-1)\beta)} &
  \implies \quad
  \hat{A}(s) 
    % &= \frac{\Delta f_m}{s \Delta m \Delta g_m}
    %   \brk{\frac{\sqrt{(f_m - \mu)(f_m - g_m)} 
    %               + \sqrt{(\mu - 1)(g_m - 1)}}
    %             {\sqrt{(f_m - g_m)(g_m - 1)} 
    %               + \sqrt{(f_m - \mu)(\mu - 1)}}}^2.
    &= \frac{S(m\beta) - S((m-1)\beta)}{s\prn{D + 1}^2} ,
\end{aligned}
\end{equation}
%
where \( D = \sqrt{(m-1)S(m\beta) - m S((m-1)\beta)} \).
The result is plotted in \cref{fig:sticky}.

@@

We will phrase it in terms of \(\snrb(\tau)\), reintroducing \(r\):
%
\begin{equation}\label{eq:envunits}
  \snrb(\tau) = \frac{ \sqrt{N} \hat{A}\prn{\frac{1}{r\tau}} }{ r\tau },
  \qquad
  \beta(\tau) = \sinh\inv \!\!\sqrt{1/2r\tau}.
\end{equation}
%
Then, combining \cref{eq:binaryenv,eq:unienv,eq:stickylaplace}, 
% using the notation \( \Delta_{\varepsilon}[T(M)] = T(M) - \varepsilon T(M-2) \) for any function \(T(M)\), 
we find
%
\begin{equation}\label{eq:henv}
  \snrb(\tau) = \left\{
\begin{aligned}
  & \frac{\sqrt{N}}{1+r\tau}, &
  & r\tau \leq \tfrac{1}{2\sinh^2\frac{y_*}{2}} , \\
  & \sqrt{N} \prn{\frac{ \sinh y_* }{ \cosh^2 y_* }} \beta(\tau), &
  \tfrac{1}{2\sinh^2 \frac{y_*}{2}} \leq & r\tau \leq \tfrac{1}{2\sinh^2 \frac{y_*}{M}} , \\
  & \frac{\sqrt{N}\brk{S\prn{\tfrac{M\beta}{2}} - S\prn{\tfrac{(M-2)\beta}{2}}}}
        {\brk{\sqrt{{\frac{M-2}{2} S\prn{\tfrac{M\beta}{2}} - \frac{M}{2} S\prn{\tfrac{(M-2)\beta}{2}}}} + 1}^2} , &
  % & \max_{\varepsilon \in [0,1]} \brc{
  %     \frac{2\sqrt{N}(1-\varepsilon) \Delta_{\varepsilon}\brk{S\prn{\tfrac{M\beta}{2}}}}
  %     {\Delta_{\varepsilon}\brk{M} \Delta_{\varepsilon}\brk{S\prn{\tfrac{M\beta}{2}} + 1} } 
  %     }, &
  \tfrac{1}{2\sinh^2 \frac{y_*}{M}} \leq & r\tau ,
\end{aligned}
\right.
\end{equation}
%
where \(S(\beta) = \cosh \beta(\tau) - 1\) (see \cref{eq:detagensol}) and \(y_*\) is defined in \cref{eq:unienv}.

For \(M \gg 1\), and \(r\tau\) much greater than the lower bound of each region, we can approximate the envelope as
%
\begin{equation}\label{eq:henvapprox}
  \snrb(\tau) \approx \left\{
\begin{aligned}
  & \frac{\sqrt{N}}{1+r\tau}, &
  & r\tau \leq 0.73 , \\
  & \frac{ 0.54\sqrt{N}}{ \sqrt{r\tau} } , &
  0.73 \leq & r\tau \leq 0.22 M^2 , \\
  & \frac{ \sqrt{N} (M-1) }{ r\tau }, &\quad
  0.22 M^2 \leq &r\tau .
\end{aligned}
\right.
\end{equation}
%
This is plotted in \cref{fig:heuristicenv}.
It should be compared to \cref{eq:env,eq:envDB}.
\Cref{eq:henvapprox} has a similar form to the theoretical envelope in \cref{eq:envDB}.
The left edge of the middle section is at later times in the theoretical version if \(\gamma \gtrsim \frac{1}{2} \csch^2 \frac{y_\ast}{2} \approx 0.73 \).
The right edge of the middle section is at later times in the theoretical version if \(\gamma \lesssim 2 y_\ast^2 \approx 4.53 \).
The middle section has greater \(\snrb\) in the theoretical version if \(\gamma \gtrsim \frac{8\sinh^2y_\ast}{\cosh^4y_\ast} \approx 1.18 \).
